\begin{rubric}{Education}
%
\entry*[2018-07 -- 2024-07]%
    \textbf{Ph.D. in Mechanics, Xi'an Jiaotong University, Xi'an, China. School of Aerospace Engineering (CGPA: \textit{3.74/4})}.
    \par \textbf{Thesis Title}: \emph{Numerical Modelling of an Air-in-Liquid Compound Drop}.
    \par \textbf{Advisor}: \textbf{Prof. Marie-Jean THORAVAL}
    \par \textbf{Description}: \emph{Focused on the dynamics of hollow drops, with applications in plasma spraying of thermal barrier coatings and sea spray aerosols. Investigated force balance and counter-jet phenomena using theoretical models and the open-source CFD tool Basilisk. Performed direct numerical simulations on HPC clusters.}
%
\entry*[2017-09 -- 2018-06]%
    \textbf{Chinese Language Course, Xi'an Jiaotong University, Xi'an, China.} \textit{HSK Level 3 certified}.
%
\entry*[2013-07 -- 2015-07]%
    \textbf{M.Tech. in Computational Fluid Dynamics, UPES Dehradun (CGPA: \textit{3.02/4})}.
    \par \textbf{Thesis Title}: \emph{Incompressible Flow Simulation in a Channel with a Square Cylinder Using FORTRAN}.
    \par \textbf{Advisor}: \textbf{Dr. K.P. Singh, ADA Bangalore}
    \par \textbf{Description}: \emph{Studied the impact of channel aspect ratio on square cylinder wakes using exit velocity profiles at various inlet distances. Developed an in-house FORTRAN flow solver validated against cavity benchmarks, with results compared to experimental and numerical data.}
%
\entry*[2006-07 -- 2010-07]%
    \textbf{Bachelor in Mechanical Engineering, North Maharashtra University, Jalgaon (Percentage: \textit{68.20\%}, CGPA: \textit{2.73/4.00})}.
    \par \textbf{Thesis Title}: \emph{Flow Analysis in Refrigerator Tubing}.
%
\entry*[2006 -- 2007]%
    \textbf{Higher Secondary Certificate (HSC), Maharashtra State Board. (Percentage: \textit{65.50\%}, CGPA: \textit{2.62/4.00})}.
%
\entry*[2004 -- 2005]%
    \textbf{Secondary School Certificate (SSC), Maharashtra State Board. (Percentage: \textit{77.20\%}, CGPA: \textit{3.09/4.00})}.

\end{rubric}

