\begin{rubric}{Employment History}
%
\entry*[2025-08 -- Present]%
    \textbf{Postdoctoral Researcher}
    {\href{https://www.zju.edu.cn/}{\textbf{Zhejiang University, China}}}
    \par \textbf{Department}: \emph{College of Biosystems Engineering and Food Science}
    \par \textbf{Project Title}: \emph{Application of CFD in Recirculating Aquaculture Systems (RAS)}
    \par \textbf{Advisor}: \emph{\textbf{\href{https://person.zju.edu.cn/0618129}{Prof. Zhao Jian}} (College of Biosystems Engineering and Food Science)}
    \par \textbf{Responsibilities}: \emph{Develop and apply CFD models to simulate and optimize water flow, temperature, and waste dispersion within RAS tanks and filtration units. Analyze hydrodynamics to ensure optimal water quality, fish welfare, and efficient removal of metabolites and particulate matter. Provide data-driven design recommendations for system components to enhance performance, reduce energy consumption, and support sustainable production. Utilize Basilisk open-source CFD software for grid-adaptive multiphase flow simulations.}
%
\entry*[2025-04 -- 2025-07]%
    \textbf{Research Associate}
    {\href{https://www.iith.ac.in/}{\textbf{Indian Institute of Technology Hyderabad, India}}}
    \par \textbf{Department}: \emph{Department of Mechanical and Aerospace Engineering, and Department of Chemical Engineering}
    \par \textbf{Project Title}: \emph{Non-Spherical Aerodynamic Breakup of Droplets Using DNS}
    \par \textbf{Advisors}: \emph{\textbf{\href{https://iith.ac.in/mae/sbehera/}{Prof. Sachidananda Behera}} (Mechanical and Aerospace Engineering), \textbf{\href{https://www.iith.ac.in/che/ksahu/}{Prof. Kirti Chandra Sahu}} (Chemical Engineering)}
    \par \textbf{Responsibilities}: \emph{Conduct high-fidelity direct numerical simulations (DNS) of aerodynamic droplet breakup and analyze breakup regimes under varying Weber and Reynolds numbers. Utilize Basilisk open-source CFD software for grid-adaptive multiphase flow simulations.}
%
\entry*[2024-07 -- 2025-03]%
    \textbf{Product Development Engineer (CFD)}
    {\href{https://www.lingyiitech.com/}{\textbf{Guangdong Lingyi iTECH Manufacturing Co. Ltd., Shenzhen, China}}}
    \par \textbf{Responsibilities}: \emph{Perform CFD simulation and optimization of vapor chambers using ANSYS Fluent and Basilisk open-source CFD software. Conduct simulation and validation of thermal designs for vapor chambers in mobile phone products. Develop and implement User-Defined Functions (UDFs) for vapor chamber modeling.}
%
\entry*[2016-10 -- 2017-06]%
    \textbf{Junior Research Fellow}
    {\href{https://www.me.iitb.ac.in/}{\textbf{Indian Institute of Technology Bombay, India}}}
    \par \textbf{Advisors}: \emph{\textbf{\href{https://sites.google.com/site/amitabhresearch/home}{Prof. Amitabh Bhattacharya}} (IIT Bombay), \textbf{\href{https://www.ctfluids.com/ctf_team/tuantran/}{Prof. Tuan Tran}} (National University of Singapore)}
    \par \textbf{Responsibilities}: \emph{Conduct research on nucleate boiling on passive and active flexible micro-structured surfaces using an in-house CFD solver. Debug and verify two-phase simulations against theoretical solutions. Perform systematic numerical simulations and experiments using high-speed imaging.} 
%
\entry*[2015-08 -- 2016-09]%
    \textbf{Junior Research Fellow}
    {\href{https://www.diat.ac.in/applied-mathematics/}{\textbf{Defence Institute of Advanced Technology, Pune, India}}}
    \par \textbf{Advisor}: \emph{\textbf{\href{https://www.diat.ac.in/view-profile/?id=115}{Dr. D. Srikanth}}}
    \par \textbf{Responsibilities}: \emph{Perform CFD two-phase simulations for non-Newtonian flow. Conduct data processing using MATLAB and GNUplot. Perform post-processing using Tecplot.}
%
\entry*[2010-08 -- 2013-06]%
    \textbf{Production Engineer}
    {\href{https://www.bharatforge.com/}{\textbf{Bharat Forge Ltd., Pune, India}}}
    \par \textbf{Responsibilities}: \emph{Perform and deliver structural analysis using finite element analysis. Conduct FEA and propose optimization solutions. Act as a bridge between die design and production engineering departments. Contribute to the development and documentation of structural simulation methodologies. Support designers in establishing certification and validation plans.}
\end{rubric}
